\vspace{1.0cm} \LARGE \bf fluB

### 2013-05-31 fluB.tex
Replacing references to subtypes with references to lineages.

\subsection*{Sequences and subtyping}
We compiled a dataset of 452 complete influenza B genomes from GISAID (comment - need acknowledgment tables). 
Each strain was assigned to a lineage (either Vic or Yam subtype) in each segment by making maximum likelihood trees and looking whether it fell within the subtree containing B/Victoria/02/87 or B/Yamagata/16/88 sequences with the exception of the NS segment (B/Victoria/02/87 was a reassortant and possessed a Yam lineage NS), where B/Norway/1/84 was considered as being representative of Victoria lineage.
Each strain was thus assigned 8 lineages depending on the combination of lineages it belongs to in all trees (for example all segments except for NS in strain B/Victoria/02/87 belong to Vic lineage and can thus be represented as V,V,V,V,V,V,V,Y). 
Seven of these where then used as discrete states in each of the trees (e.g. PB1 tree had PB2, PA, HA, NP, NA, MP and NS as traits and V or Y as trait values) in BEAST (comment - reference BEAST). (comment - give figure with proportions of subtypes for each segment)

>>>>

\subsection*{Sequences and subtyping}
We compiled a dataset of 452 complete influenza B genomes from GISAID (comment - need acknowledgment tables). 
Each strain was assigned to a lineage (either Vic or Yam) in each segment by making maximum likelihood trees and looking whether it fell within the subtree containing B/Victoria/02/87 or B/Yamagata/16/88 sequences with the exception of the NS segment (B/Victoria/02/87 was a reassortant and possessed a Yam lineage NS), where B/Norway/1/84 was considered as being representative of Victoria lineage.
Each strain was thus assigned 8 lineages depending on the combination of lineages it belongs to in all trees (for example all segments except for NS in strain B/Victoria/02/87 belong to Vic lineage and can thus be represented as V,V,V,V,V,V,V,Y). 
Seven of these where then used as discrete states in each of the trees (e.g. PB1 tree had PB2, PA, HA, NP, NA, MP and NS as traits and V or Y as trait values) in BEAST (comment - reference BEAST). (comment - give figure with proportions of each lineage for each segment)
